Parameter estimation

### 2023-06-28 SFE-article/Sections/Results.tex
28.06

	\begin{table}[!h]
		\centering
		\adjustbox{max width=\columnwidth}{%
		\begin{tabular}{ lccccccc }
			\hline 
			Parameter		&$k_m$[-] 	& $D_i$[m/s$^2$] 	& $D_e^M$[m/s$^2$]	& $\Upsilon$ [m$^3$/kg] & $m_{total}$[g]	& $\tau$[-] 	& $\sigma$[-] \\  \hline
			Lower bound		&0	  		& 0 	  			& 0 				&	0					& 80 		 		& 0 	   		& 0 \\ 
			Upper bound		&$+\infty$	& $+\infty$ 		& $+\infty$			&	100					& 150 				& 1 			& $+\infty$ \\ 
			Initial guess	&1e5 		& 3 	  			& 1 				&	0					& 80 		 		& 0.65 	   		& 0.1 \\  \hline
		\end{tabular} }
	\caption{Constraints and initial guess of the parameter estimation problem}
	\label{tab:Constraints}
	\end{table}

@@

	Figure \ref{fig: estimation_results} show yield curves for each of experiments. The blue dots indicate the data point obtained as a measurement from the laboratory experiments. The black curve represents the yield curve obtained from the initial guess of the parameters. The blue curve correspond to yield curve obtained as a solution of the optimization problem. The curves on the left hand-side of the Figure \ref{fig: estimation_results}, are the cumulative yield curves, which represents the cumulative amount of the oil collected during each experiment. The plots on the right hand-side, represent the derivative of the cumulative yield curves. As explained in the chapter \ref{CH: Parameter_estimation}, the derivatives of the cumulative measurements are independent on the previous measurement and should be used for the parameter estimation.

@@

	The results of parameter estimation can be found in Table \ref{tab: Estimation_results} and the concentration profiles, which correspond for the optimized solution for each experiments, are presented on Figure \ref{fig: estimation_results_profiles} in Appendix \ref{CH: Profiles}. As can be noticed, the optimizer found that the partition factor should be as high as possible. Such a behaviour suggest that the solvent is far from the saturation, and the model can be simplified. The model reduction can be introduced by considering the limit of the concentration gradient

@@

	Values of the internal diffusion coefficients are distinguished for each experiment, which grows as the fluid density increase. The order of magnitude of $D_i$ obtained from the optimization is similar to values found by other researchers. \citet{Reverchon1996} performed the parameter estimation for the extraction process of sage oil from seeds and reported $D_i \approx 6e-13$.

@@

	The $\Upsilon$ coefficient

@@

	\begin{figure}[!h]
		\centering
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T40_P200.pdf}
			\caption{Experiment at $40^\circ C$ and $200$ bar}
		\end{subfigure}
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T50_P200.pdf}
			\caption{Experiment at $50^\circ C$ and $200$ bar}
		\end{subfigure}
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T40_P300_org.pdf}
			\caption{Experiment at $40^\circ C$ and $300$ bar}
		\end{subfigure}
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T50_P300_org.pdf}
			\caption{Experiment at $50^\circ C$ and $300$ bar}
		\end{subfigure}
		\caption{Results of parameter fitting, with estimation of the initial state}
		\label{fig: estimation_results}
	\end{figure}

@@

	The results of the linear regression applied to $D_i$ and $D_e^M$ are presented in Figure \ref{fig:Regression_1}. It can be observed that the internal diffusion coefficient increases with increasing fluid density, while the axial diffusion coefficient decreases.

	The increase in the density of the supercritical fluid can lead to an increase in the solubility of the solute and, consequently, an increase in the concentration gradient. This increased concentration gradient drives the solute to diffuse more rapidly through the matrix of the solid particles, resulting in an increased internal mass transfer coefficient. However, the effect of increased solubility on the internal mass transfer coefficient outweighs the resistance from higher density, resulting in an overall increase in the internal mass transfer coefficient with density. The same behaviour can be observed in Figure \ref{fig: estimation_results}, where plots on the right-hand side exhibit a peak. The higher the peak, the greater the increase in solute concentration in the fluid phase, which can be explained by higher solubility.

	The behaviour of the axial diffusion coefficient can be explained through Graham’s Law of Diffusion, which states that the rate of diffusion of a molecule is inversely proportional to the square root of its density under given conditions of temperature and pressure. This means that denser media slow down the axial diffusion rate of molecules.

	{\color{red}IDEAL I SHOULD SUPPORT THIS EXPLANATION WITH SOME REFERENCES}

	Figure \ref{fig:Regression_2} show the result of fitting a second-order polynomial in density space. It can be observed that the fit obtained from quadratic functions seems to be represent both dataset better.

	The experimental procedure and the used device can influence the values of $\tau$ and $\sigma$. Therefore, seeking a general expression for the initial state that is solely a function of operating conditions may not be sufficient to fully describe the relationship between these parameters. However, if first- and second-order regressions are applied to $\tau$ and $\sigma$, some general conclusions about the trend can be drawn. The results of the regression applied to $\tau$ and $\sigma$ are presented in Figure \ref{fig:Regression_tau_simga}.

	\begin{figure}[!h]
		\centering
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 18.8cm 8cm 2.5cm 7.6cm,clip,width=0.49\textwidth]{/Results_estimation/Trend_Lines_order_1.pdf}
			\includegraphics[trim = 4cm 2cm 17.5cm 13.6cm,clip,width=0.49\textwidth]{/Results_estimation/Trend_Lines_order_1.pdf}
			\caption{First order polynomial regression of fitted parameters ($\tau$ and $\sigma$) as a function of fluid density $\rho_f$}
			\label{fig:Regression_3}
		\end{subfigure}
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 18.8cm 8cm 2.5cm 7.6cm,clip,width=0.49\textwidth]{/Results_estimation/Trend_Lines_order_2.pdf}
			\includegraphics[trim = 4cm 2cm 17.5cm 13.6cm,clip,width=0.49\textwidth]{/Results_estimation/Trend_Lines_order_2.pdf}
			\caption{Second order polynomial regression of fitted parameters ($\tau$ and $\sigma$) as a function of fluid density $\rho_f$}
			\label{fig:Regression_4}
		\end{subfigure}
		\caption{Regression of $\tau$ and $\sigma$} 
		\label{fig:Regression_tau_simga}
	\end{figure}

	As can be seen from Figure \ref{fig:Regression_tau_simga} , the $\tau$ seems to decrease as the fluid density increase. The standard deviation increases as the fluid density increase. As mentioned above, these results should be used with caution due to uninvestigated influence of the equipment on the extraction results.

	To prove that the obtained solution is a global solution, the parameter estimation problem was run from multiple initial conditions. The Appendix \ref{CH: Profiles_2}, contain a solution of the optimization solution and corresponding figures.

>>>>

	\begin{table}[!h]
		\centering
		\adjustbox{max width=\columnwidth}{%
		\begin{tabular}{ lccccccc }
			\hline 
			Parameter		&$k_m$[-] 	& $D_i$[$m^2/s$] 	& $D_e^M$[$m^2/s$]	& $\Upsilon$ [m$^3$/kg] & $m_{total}$[g]	& $\tau$[-] 	& $\sigma$[-] \\  \hline
			Lower bound		&0	  		& 0 	  			& 0 				&	0					& 80 		 		& 0 	   		& 0 \\ 
			Upper bound		&$+\infty$	& $+\infty$ 		& $+\infty$			&	100					& 150 				& 1 			& $+\infty$ \\ 
			Initial guess	&1e5 		& 3 	  			& 1 				&	0					& 80 		 		& 0.65 	   		& 0.1 \\  \hline
		\end{tabular} }
	\caption{Constraints and initial guess of the parameter estimation problem}
	\label{tab:Constraints}
	\end{table}

@@

	Figure \ref{fig: estimation_results} show yield curves for each of experiments. The blue dots indicate the data point obtained as a measurement from the laboratory experiments. The black curve represents the yield curve obtained from the initial guess of the parameters. The blue curve correspond to yield curve obtained as a solution of the optimization problem. The curves on the left hand-side of the Figure \ref{fig: estimation_results}, are the cumulative yield curves, which represents the cumulative amount of the oil collected during each experiment. The plots on the right hand-side, represent the derivative of the cumulative yield curves. As explained in the Chapter \ref{CH: Parameter_estimation}, the derivatives of the cumulative measurements are independent on the previous measurement and should be used for the parameter estimation.

@@

	The results of parameter estimation can be found in Table \ref{tab: Estimation_results} and the concentration profiles, which correspond for the optimized solution for each experiments, are presented on Figure \ref{fig: estimation_results_profiles} in Appendix \ref{CH: Profiles}.

	\begin{figure}[!h]
		\centering
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T40_P200.pdf}
			\caption{Experiment at $40^\circ C$ and $200$ bar}
		\end{subfigure}
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T50_P200.pdf}
			\caption{Experiment at $50^\circ C$ and $200$ bar}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T40_P300_org.pdf}
			\caption{Experiment at $40^\circ C$ and $300$ bar}
		\end{subfigure}
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T50_P300_org.pdf}
			\caption{Experiment at $50^\circ C$ and $300$ bar}
		\end{subfigure}
		\caption{Results of parameter fitting, with estimation of the initial state}
		\label{fig: estimation_results}
	\end{figure}

	As can be noticed, the optimizer found that the partition factor should be as high as possible. Such a behaviour suggest that the solvent is far from the saturation, and the model can be simplified. The model reduction can be introduced by considering the limit of the concentration gradient

@@

	Values of the internal diffusion coefficients are distinguished for each experiment. The order of magnitude of $D_i$ obtained from the optimization is similar to values found by other researchers. \citet{Reverchon1996} performed the parameter estimation for the extraction process of sage oil from seeds and reported $D_i \approx 6e-13$. The $\gamma$ (Equation \ref{EQ: C_sat_function}) coefficient multiply the reference value of $D_i$ to take into consideration that solute inside of a particle is harder to obtain than the solute close to the outer surface, as explained before. The Figure \ref{fig:Di_upsilon_res} shows how the internal diffusivity as a function of the solute's concentration in the solid phase. It can be observed that the obtained values of $D_i$ increase as the density increase. This behaviour can be explained by an increase in solubility when the density grow. \citet{Shojaie2010}, proved that the carvone (which is one of the main components of caraway oil) solubility increase together with pressure increase and decrease when temperature increase.

	\begin{figure}
		\centering
		\includegraphics[trim = 2cm 0.4cm 2cm 0.5cm, clip, width=\columnwidth]{/Results_estimation/D_i_Uppsilon_results.pdf}
		\caption{The dependence of the internal diffusion coefficient on the solutes concentration in the solid phase}
		\label{fig:Di_upsilon_res}
	\end{figure}

@@

@@

@@
